Concurrent Programming in Harmony

### 2020-12-27 book/paper.tex
Renamed process to thread

\index{binary semaphore}
Locks are a special case of \emph{binary semaphores}.
Like locks, binary semaphores are either in an \emph{acquired} state
or a \emph{released} state.
Processes trying to acquire an already acquired binary semaphore
have to wait until the binary semaphore is released.
It is illegal to release a binary semaphore that is in a released
state.
A lock is a binary semaphore that, by convention, is initialized to a
released state, and is always released by the same thread that acquired it.
A binary semaphore can be initialized to an acquired state and can be
released by threads other than the thread that last acquired the
binary semaphore.

@@

When leaving the critical section, the thread must open exactly one
of the gates, but it does not have to be the gate that it used to enter
the critical section.
In particular, when a thread leaves the critical section it should
check for each waiting gate if its waiting condition hold and if there are
processes trying to get through the gate.  If there is such a gate,
it must select one and open that gate.  If there is no such gate,
it must open the main gate.

@@

The modes of a context are as follows:

>>>>

\index{binary semaphore}
Locks are a special case of \emph{binary semaphores}.
Like locks, binary semaphores are either in an \emph{acquired} state
or a \emph{released} state.
Threads trying to acquire an already acquired binary semaphore
have to wait until the binary semaphore is released.
It is illegal to release a binary semaphore that is in a released
state.
A lock is a binary semaphore that, by convention, is initialized to a
released state, and is always released by the same thread that acquired it.
A binary semaphore can be initialized to an acquired state and can be
released by threads other than the thread that last acquired the
binary semaphore.

@@

When leaving the critical section, the thread must open exactly one
of the gates, but it does not have to be the gate that it used to enter
the critical section.
In particular, when a thread leaves the critical section it should
check for each waiting gate if its waiting condition hold and if there are
threads trying to get through the gate.  If there is such a gate,
it must select one and open that gate.  If there is no such gate,
it must open the main gate.

@@

The possible modes of a context are as follows:
